Nanophotonic Computational Design

### 2013-02-23 defense/pres3.tex
Getting there...

\I  Realization: Design-by-description is \emph{extremely powerful}
\pause
    \BI The description (or function) of all useful devices is known
    \I  Therefore, design-by-description will allow us to design \emph{everything} 
    \EI
\pause
\I  Assumes that design-by-description can actually be made to work
\pause
\I  Our goal: Make it work

@@

\oursection{Summary}
\smallfig{takeaway}
\I  Our work: Software to design 3D linear nanophotonic devices using 
    the full available parameter space \pause
\nextpage

\I  Many of these devices are
    \BI Completely novel (no previously known designs)
    \I  Extremely compact (footprints of a few vacuum wavelengths)
    \I  High efficiency ($>80\%$ transmission) \EI
\pause

\I  Developed by
    \BI applying (convex) optimization techniques (math)
    \I  to the area of nanophotonics (physics)
    \I  and implementing in software (programming) \EI
\pause

@@

\oursection{Given a field, can we find its structure?}
\smallfig{my_definition}
\stepwise{
\step{\I  Equivalently, find $\epsilon$ (structure) given $E$ (field)
    \BE \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
        -i \omega J \EE}
\step{\I  If possible, we can design \emph{any} nanophotonic/optical component!}
}
\nextpage

\I Answer: Yes, given $E$ we \emph{can} solve for $\epsilon$ (trivial!)
    \stepwise{
    \begin{align*} 
    \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E &= 
        -i \omega J \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\\
    \step{\omega^2 \epsilon E &= \nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J }\\
    \step{\omega^2 E \epsilon &= \nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J }\\
    \step{\epsilon &= (\nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J)/ \omega^2 E} 
    \end{align*}
    }
\I  Solving for $\epsilon$ actually way faster than simulation (solving for $E$)!
\nextpage

@@

\I  Choose canonical 1D cavity field for $x$
\I  Solve for $z$ (structure) and check design fidelity with simulation
\smallfig{1d_leastsquares}
\pause
\I  Result
    \BI Perfect performance
    \I  But unmanufacturable structure ($z$ not well-behaved) \EI
\nextpage

>>>>

\I  Realization: Design-by-description is \emph{extremely powerful}
\pause
    \BI The description (or function) of all useful devices is known
    \I  Therefore, design-by-description enables the design of \emph{everything} 
    \EI
\pause
\I  Assumption: Design-by-description can actually be made to work
\pause
\I  Our goal: Make it work!

@@

\oursection{Summary}
\smallfig{takeaway}
\I  Our work: Designed 3D linear nanophotonic devices
    \BI Using the full parameter space
    \I  Using design-by-description \EI
\nextpage

\I  Many of these devices are
    \BI Completely novel (no previously known designs)
    \I  Extremely compact (footprints of a few vacuum wavelengths)
    \I  High efficiency ($>80\%$ transmission) 
    \I  Manufacturable \EI
\pause

\I  Our approach:
    \BI applying (convex) optimization techniques (math)
    \I  to the area of nanophotonics (physics)
    \I  and implementing in software (programming) \EI
\pause

@@

\oursection{Given a field, can we find its device/structure?}
\smallfig{my_definition}
\stepwise{
\step{\I  Equivalently, find $\epsilon$ (structure) given $E$ (field)
    \BE \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
        -i \omega J \EE
where $\epsilon = \vec{\epsilon}(r), E=\vec{E}(r), J = \vec{J}(r)$}
}
\nextpage

\oursection{Given a field, can we find its device/structure?}
\I  Answer: Yes, given $E$ we \emph{can} solve for $\epsilon$ (trivial!) \\
    \stepwise{
    \begin{align*} 
    \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E &= 
        -i \omega J \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\\
    \step{\omega^2 \epsilon E &= \nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J }\\
    \step{\omega^2 E \epsilon &= \nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J }\\
    \step{\epsilon &= (\nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J)/ \omega^2 E} 
    \end{align*}
    (Reminder, $\epsilon = \vec{\epsilon}(r), E=\vec{E}(r), J = \vec{J}(r)$)
\step{
\I  Solving for $\epsilon$ actually way faster than simulation (solving for $E$)!
}

    }
\nextpage

@@

\I  Choose canonical 1D cavity field for $x$
\I  Solve for $z$ (structure) and check design fidelity with simulation
\smallfig{1d_leastsquares}
\pause

\let\thefootnote\relax\footnotetext{Footnotetext without footnote mark} 
\I  Result\footnote{Lu et al, Optics Express (2010)}: 
    Perfect performance, but unmanufacturable structure ($z$)
\nextpage
